Experiences designing and building a PRAGMA Cloud Scheduler

### 2015-08-13 paper.tex
Latest version.

PRAGMA had the following three key requirements for a cloud testbed scheduler:

@@

\textbf{Scale to tens of users:}  While the PRAGMA community was composed of nineteen active institution sites in 2014, the number of expected users for the cloud testbed is in the tens of users, not hundreds nor thousands.  Therefore, our scheduler can be simplified and we can give high priority to the requirements of low participation overhead and easy of use.

% enable varying -- time limited -- not get bogged down by deployment of technologies

% view available resources and scientific application virtual machines
\section{Scheduler Design}
\label{Sec:Design}

Users can request access to resources similar to requesting a room (i.e., a room reservation system)
PCC would be used to automatically start and monitor user's VMs slash VC via pragma\_boot up at sites 
Only support 10s of users

Repeat longer version of text in abstract with appropriate citations.

Discuss requirements and technologies like pragma boot, etc.

ENT
one controller at participating site
way to slice switch? specialized controller? 
AutoVFlow by Hiroaki Yamanaka (NICT)
For users interested in running VMs, cloud middleware (OpenStack, CloudStack, etc) should take care of the slicing.
 Recurring problem: users tend to forget and leave idle VMs running.
For users interested in cloud middleware research/development, and/or access to bare-metal hardware (e.g., ENT), scheduling of resources and coordination among users will be needed.
Network slicing technologies (Auto-VFlow, FlowVisor, FlowSpace Firewall, etc) when deployed could help
Use PBS as a scheduler (or Condor or Slurm?)
Nimbus have a module that interfaces with PBS
 Use PBS to schedule interactive sessions on bare metal
Use a shared calendar so that users can make resource reservations (`a la Grid?5000)
ORCA from GENI/Planetlab? 
Leases

Discuss process of narrowing down scheduler design from meeting ideas 
(e.g., batch scheduler, Grid 5000, GENI, Google doc, DHCP leases).

\section{Calendaring systems}
\label{Sec:Calendars}

@@

Thank Mauricio and Jose.

>>>>

PRAGMA had the following three key requirements for a cloud testbed scheduler to enable multiple users access to the resources at a time:

@@

\textbf{Scale to tens of users:}  While the PRAGMA community was composed of nineteen active institution sites in 2014, the number of expected users for the cloud testbed is in the tens of users, not hundreds nor thousands.  Therefore, we can prioritize simplicity over scalability and give higher priority to the requirements of low participation overhead and easy of use.

\section{Scheduler Design}
\label{Sec:Design}

In our design discussions, we first looked at the below existing solutions that could be adapted for PRAGMA's scheduling needs:

\textbf{Existing HPC schedulers}:  Open source batch schedulers like Slurm~\cite{slurm}, TORQUE~\cite{torque}, and HTCondor are commonly used in  HPC to manage space shared resources.  While these batch schedulers  are widely used, they either do not work across multiple sites (TORQUE) or are too heavy weight for what PRAGMA needs, requiring custom configuration and multiple daemons at each site (Slurm and HTCondor).  Furthermore, PRAGMA users change over time and we wanted a low barrier to entry like a simple Web based interface for scheduling, rather than the command-line tools and queue abstractions that these batch schedulers provide.

\textbf{Grid'5000:}   NEEDS TO BE WRITTEN.  Add short description of Grid'5000.  They use OAR which is a batch scheduler similar to above and the calendar gui called GridPrems is one of three options for interacting with Grid'5000.  A key difference is that testbed resources are dedicated rather than like on PRAGMA where they could be shared;  I believe also single admin model.  Interesting set of tools.  We can say we liked their calendar approach the best.

\textbf{DHCP Leases:}  NEEDS TO BE WRITTEN.

\textbf{GENI/PlanetLab}:  NEEDS TO BE WRITTEN.  ORCA

Out of these approaches, we liked the Grid'5000 calendar reservation interface, GridPrems, for scheduling the best.  The calendar reservation scheduling is an interface that all users are familiar with in their everyday lives and would be well suited to the different PRAGMA users who have varying levels of cloud expertise.

\section{Calendar systems}
\label{Sec:Calendars}

In addition to GridPrems interface, we decided to look at other calendar reservation systems.

@@

The authors would like to thank Jose Fortes and Mauricio Tsugawa for their help during our initial design discussions and for providing resources at University of Florida during development.
